Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-16 ltx/data_paper/DataPaper.tex
started to edit results section

This section demonstrates the identification of the proposed IDE model using simulated data. The observation noise and the field disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the connectivity kernel. Data was generated employing state-space equation (\ref{eq:LS-finalformstatespacemodel}-\ref{eq:LS-QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5$~mm) basis functions with $\sigma_{\phi}^2=1.58$~mm$^2$, assuming the observed field can be fully described by the decomposed IDE model. 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach the steady state. The observation noise variance was set to 0.2. All the other parameters for the simulation were chosen as that of Chapter~\ref{LSChapter} (see Table~\ref{tab:LS-Parameters}).

\subsection{Correlation analysis}

>>>>

In this section, a demonstration of the estimation framework for the proposed IDE neural field model is provided. To demonstrate the estimation procedure, simulated data is used to establish a ground truth for a comparison. The parameters of the observation noise and the field disturbance were assumed to be unknown, and therefore, were inferred from data. to the estimation algorithm and no assumption were made on the shape of the connectivity kernel. Data was generated employing state-space equation (\ref{eq:LS-finalformstatespacemodel}-\ref{eq:LS-QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5$~mm) basis functions with $\sigma_{\phi}^2=1.58$~mm$^2$, assuming the observed field can be fully described by the decomposed IDE model. 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach the steady state. The observation noise variance was set to 0.2. All the other parameters for the simulation were chosen as that of Chapter~\ref{LSChapter} (see Table~\ref{tab:LS-Parameters}).

\subsection{Correlation Analysis}
